Meta-analysis

### 2019-10-31 04_Prep_data.Rmd
Edits reviewed and accepted
Correct data source to OneDrive link

```{r}
library(dplyr)
library(openxlsx)
library(kableExtra)
library(ggplot2)
library(leaflet)
#source("./getPPD2.R")

```

```{r Calculate_yield-gains}
PM_MB_means <-
   read.csv("data/1902 powdery mildew-Mungbean - Collated means.csv",
            stringsAsFactors = FALSE)
PM_MB_means$grain_yield.t.ha. <-
   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data

>>>>

Warning this markdown file needs corrections to variable names.
Column headers for PM_MB_means were changed and the column names need to be corrected below accordingly

```{r}
library(dplyr)
library(readr)
```

```{r Calculate_yield-gains}
source("R/import_data.R")
PM_MB_means <- import_data()

PM_MB_means$grain_yield.t.ha. <-
   as.numeric(PM_MB_means$grain_yield.t.ha.) # NAs produced due to some cells having text description to why there is no specific data
